---
title: "Case Study 1"
author: "Ben Tanaka"
date: "6/22/2019"
output: 
  html_document:
    keep_md: true
---

# **Introduction**
** Enter introduction 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/users/ben/documents/r/Case_Study_1")
getwd()

library(xml2)
library(rvest)
library(stringr)
library(tibble)
library(data.table)
library(knitr)
library(kableExtra)
library(dplyr)
library(tidyr)
library(ggplot2)
```


## Step 1:  Import of data sets
* This will import the two data sets Beers.csv and Breweries csv and view the first 5 lines of the data in order to determine how to join the two data sets.  When doing a quick view of the two data sets it appears that both have headers in the first row the the separator is using a comma.  Beers.csv will be imported as df_Beers and Breweries will be imported as df_breweries.  This will also output the table.

```{r Import and Review}
df_Beers <- read.csv(file="beers.csv", header=TRUE, sep=",")
df_Breweries <- read.csv(file="breweries.csv", header=TRUE, sep=",")
head(df_Beers)
head(df_Breweries)
```

## Exactly how many breweries are present in each state
* This step will take the df_breweries data frame and count by the states as well as rename the columns
``` {r Q1}
df_Breweries_by_State <- df_Breweries %>% group_by(State) %>% tally( sort=TRUE)
setnames(df_Breweries_by_State,old=c("n"),new=c("Breweries_CNTS"))

{df_Breweries_by_State %>% kable() %>% kable_styling()}
```

* Colorado has the most breweries out of all of the states.  Seems the Water there is great for brewing beer, that or people on Colorado love their beer. 

## Beers and their Associated Breweries
* After reviewing the two data sets it appears that Brew_ID (df_Breweries) and Brewery_ID (df_Beers).  This step will merge the two tables together using the common IDs.  First we will change the name of the Brew_ID to a common name to both tables (Brewery_ID).  We also want to change the names of the columns so that they are human readable.

```{r Q2}
setnames(df_Breweries,old=c("Brew_ID"),new=c("Brewery_id"))
df_Beers_Breweries <- merge(df_Beers,df_Breweries, by=c("Brewery_id"))

setnames(df_Beers_Breweries,old=c("Name.x","Name.y"),new=c("Beer_Name","Brewery_Name"))

df_First_Six <- head(df_Beers_Breweries,6)
df_Last_Six <- tail(df_Beers_Breweries,6)

{df_First_Six %>% kable() %>% kable_styling()}
{df_Last_Six %>% kable() %>% kable_styling()}
```

## How many missing observations are there by column
*  This will show the number of observations in each column
``` {r Q3}
df_Missing_Obs <- colSums(is.na(df_Beers_Breweries))

{df_Missing_Obs %>% kable() %>% kable_styling()}
```

*  IBU has the most missing values out of all of the columnes, followed by ABV.  These are actually the only two columns that have missing data.

## What is the median Alcohol Content & International Bitterness Unit for each state
* This will group the and summarise the median for ABV & IBU as well as plot the results in decending order

``` {r Q4}
df_ABV_by_State <- df_Beers_Breweries %>% group_by(State) %>% summarise(Median=median(ABV,na.rm=TRUE))
df_IBU_by_State <- df_Beers_Breweries %>% group_by(State) %>% summarise(Median=median(IBU,na.rm=TRUE))


ggplot(df_ABV_by_State, aes(x=reorder(df_ABV_by_State$State,-df_ABV_by_State$Median), y=df_ABV_by_State$Median, fill=df_ABV_by_State$State)) + geom_bar (stat="identity") + xlab("State") + ylab("Median Alcohol by State") + ggtitle("Median Alcholol content by State")  + theme(plot.title = element_text(hjust=.5))+theme(axis.text.x=element_text(angle=90)) + scale_color_gradientn(colours=rainbow(20)) + theme(legend.position="none")

ggplot(df_IBU_by_State, aes(x=reorder(df_IBU_by_State$State,-df_IBU_by_State$Median), y=df_IBU_by_State$Median, fill=df_IBU_by_State$State)) + geom_bar (stat="identity") + xlab("State") + ylab("Median International Bitterness Unit") + ggtitle("Median International Bitterness Unit by State")  + theme(plot.title = element_text(hjust=.5))+theme(axis.text.x=element_text(angle=90)) + scale_color_gradientn(colours=rainbow(20)) + theme(legend.position="none")
```

*  Alcohol content did not vary much state by state whereas IBU did have some variation.

## States with the Maximum ABV and IBU?
*  The District of Columbia has the highest median for alochol content whereas Maine has the highest IBU.  

##  Summary statistics for ABV
*  This will show the summary statistics for ABV
``` {r q6}

summary(df_Beers$ABV,na.rm=TRUE)

```

*  The maximum ABV came to be .128 and the lowest was .00100.  I am not sure what the point of drinking that beer would be.

## Relationship between ABV and IBU
* This will plot IBU and ABV in a scatter plot

``` {r q7}

plot(df_Beers$ABV,df_Beers$IBU, main="ABV & IBU Relationships", xlab="ABV",ylab="IBU",pch=19,frame=FALSE)

```

*  There seems to be a relationship between ABV and IBU, in which, the less alcohol content there is the less bitter the beer.  

# ** Conclusion ** 

* What is the conclusion of the study.
